\documentclass[12pt]{thesis}
\usepackage{titlesec}
\setcounter{secnumdepth}{4}

\begin{document}

\title{Thesis Proposal.\\A GENERALIZED TOOL FOR DERIVING CONNECTOMES IN SUPPORT OF COMPUTATIONAL NEUROSCIENCE}

\author{David Mattie}



%%% Choose your Degree Here%%%
\msc


%%%%%Choose your program here%%%
%\program{Mathematics}
\program{Computer Science}
%\program{Statistics}


\month{August}

\year{2018}

\supervisor{Dr. Jacob Levman}

\reader{Dr. Iker Ghondra}
\reader{Dr. James Hughes}

%\firstsupervisor{Dr. Soma Body}
%\secondsupervisor{Dr. Somabody Else}

%\firstmember{Dr. First Member}
%\secondmember{Dr. Second Member}
%\thirdmember{Dr. Third Member}
%\fourthmember{Dr. Fourth Member}
%\fifthmember{Dr. Fifth Member}

\dedication{to Dad}

%\notitlepage
%\nosignaturepage
%\nopermissionpage
%\notableofcontents
%\nolistoftables
%\nolistoffigures

\frontmatter

\begin{abstract}
This research intends to establish a framework in which to perform connectomic 
measurements of tens of thousands of data points across all major brain regions.  
A user shell will be developed to first derive these connectomes, and then provide 
mechanisms to quickly extract and analyze the calculated data of interest.  
Machine learning algorithms will demonstrate the application of computational 
neuroscience by discovering patterns consistent with autism patients.  
The objective is to provide a generalized tool that can extract data for 
multiple uses.
\end{abstract}


\begin{acknowledgements}
I would like to express my gratitude to my advisor Dr. Jacob Levman PhD, for giving 
me the opportunity for this thesis.  His sharing of knowledge across many facets of 
the material has been helpful and encouraging.  I would also like to thank 
Dr. James Hughes for his knowledge of machine learning and data mining.  Finally, 
Dr. Iker Gondra for his broad experience with image parcellation and artificial 
intelligence.
\end{acknowledgements}

\mainmatter

\include{chapter1}
%\include{chapter2}
%\include{chapter3}
%\include{chapter4}
%\include{chapter5}
%\include{chapter6}

%\bibliographystyle{alpha}
%\bibliographystyle{amsplain}
\bibliographystyle{plain}
%\bibliographystyle{these}
\addcontentsline{toc}{chapter}{Bibliography}%  This line includes Bibliography in Table of Contents
\bibliography{ref}

\end{document}
